---
title: "p8105_hw3_sl4660"
author: "Sibei Liu"
date: "2019/10/14"
output: html_document
---

```{r initial,message=FALSE}
library(p8105.datasets)
data("instacart")
library(tidyverse)
library(ggrepel)
```

# Probelm 1

## First


In the instacart dataset, there are `r ncol(instacart)` variables, `r nrow(instacart)` observations. The key variables are both order_id and product_id. Because those two can locate a piece of data. Take the first row for example, the user with id 112108, made the order with a product whose id was 49302.The product 49302 was his/her first item to add into cart, which had been reordered before. The order sequence number for this user was 4. The day she/he made this order is on Wed. And the detailed time was at 10:00.It was 9 days since her/his last order. The product--Bulgarian Yogurt is from aisle number120,which was yogurt aisle. And the product was from department number16--dairy eggs.

```{r}
aisle_number=n_distinct(select(instacart,aisle_id))

sub1=instacart %>% 
  group_by(aisle) %>% 
  summarise(n = n()) 

sub2=mutate(sub1,aisle_ranking = min_rank(desc(n))) %>% 
  arrange(aisle_ranking)
 
sub2 
```


There are `r nrow(sub2)` aisles.
The most items are from aisle ``r select(filter(sub2,aisle_ranking==1),aisle)``.

Comment: In the table above, I ranked the aisles according to the ordered items. Then I filter the aisle whose rank is 1.

## Second
```{r}
sub2%>% 
  filter(n>10000) %>% 
  ggplot(aes(x=aisle,y=n,label=n))+geom_bar(stat = "identity")+theme(axis.text.x = element_text(angle = 60, hjust=1))+scale_y_continuous(breaks =                                                      c(10000,2000,30000,40000,50000,60000,70000,80000,120000), 
    labels = c("10000","20000","30000","40000","50000","60000","70000","80000","120000"))+
   geom_text(
    aes(label = n,angle=60),
    position = position_dodge(0.9),
    vjust = 0
  )
```

Comment:By using the above table to make plot, the fresh fruits and fresh vegitables had the greatest values. Packaged vegitables followed them. The rest of products such as baby food formula, candy chocolate and so on had lower but consistent values.

## Third
```{r}
sub3=instacart %>% 
  group_by(product_id,aisle_id) %>% 
  summarize(n=n())

sub4=instacart %>% 
  group_by(product_name,aisle) %>% 
  summarize(n=n()) %>%
group_by(aisle) %>% 
  mutate(item_ranking_in_each_group = (min_rank(desc(n)))) %>% 
  arrange(aisle,item_ranking_in_each_group)

sub4_4=sub4 %>% 
  filter(aisle %in% c("baking ingredients", "dog food care","packaged vegetables fruits")&item_ranking_in_each_group<4 ) 
knitr::kable(sub4_4)
```

Comment: In baking and ingredients aisle, the light brown sugar had the highest amount. Then pure baking soda and cane sugar followed, which had amount od 387,336 respectively.
In dog food care aisle, the "Snack Sticks Chicken & Rice Recipe Dog Treats" had the highest amount, 30. Then "Organix Chicken & Brown Rice Recipe" and "Small Dog Biscuits" followed, which had amount od 28,26 respectively.
In packaged vegetables fruits aisle, the "Organic Baby Spinach" had the highest amount--9784. Then "Organic Raspberries" and "Organic Blueberries" followed, which had amount od 5546,4966 respectively.

## Fourth
```{r}
sub5=instacart %>% 
  select(product_name,order_dow,order_hour_of_day) %>% 
  filter(product_name %in% c("Pink Lady Apples","Coffee Ice Cream")) %>% 
  mutate(
    order_dow=recode(order_dow, `0`="Sun",`1`="Mon",`2`="Tue",`3`="Wed",`4`="Thur",`5`="Fri",`6`="Sat"),
    order_dow=forcats::fct_relevel(order_dow,c("Mon","Tue","Wed","Thur","Fri","Sat","Sun"))
  )  %>% 
  group_by(product_name,order_dow) %>% 
  summarise(mean_eachday_week=mean(order_hour_of_day)) %>% 
  pivot_wider(
   names_from= product_name,
    values_from= mean_eachday_week
  )
knitr::kable(sub5)
```


Comment: From Monday to Sunday, the mean hour of ordering coffee and ice cream is 14.3, 15.4, 15.3,15.2, 12.2, 13.8, 13.7 respectively. The time was focused on the beginning of afternoon.
From Monday to Sunday, the mean hour of ordering pink lady apples is 11.4, 11.7, 14.3, 11.6, 12.8, 11.9, 13.4 respectively. The time was focused around the noon.

# Problem2
```{r}
library(p8105.datasets)
data("brfss_smart2010")
```

##  Basic data cleaning
```{r}
sub6=brfss_smart2010 %>% 
  janitor::clean_names() %>% 
  filter(topic=="Overall Health") %>% 
 filter(response%in% c("Excellent","Very good","Good","Fair","Poor")) %>% 
  mutate(response = forcats::fct_relevel(response, c("Poor", "Fair", "Good","Very good","Excellent"))) 
```

## First
```{r}
sub7=sub6 %>% 
  filter(year==2002) %>% 
  group_by(locationabbr,locationdesc) %>% 
  summarise(n=n())
sub8=sub7 %>% 
  group_by(locationabbr) %>% 
  summarise(n=n()) %>% 
 filter(n>6) 
  sub8
location1=c(pull(sub8,locationabbr))

```

```{r}
sub9=sub6 %>% 
  filter(year==2010) %>% 
  group_by(locationabbr,locationdesc) %>% 
  summarise(n=n())
sub10=sub9 %>% 
  group_by(locationabbr) %>% 
  summarise(n=n()) %>% 
 filter(n>6)  
 sub10
location2=c(pull(sub10,locationabbr))
```

In 2002, `r location1` have 7 and above locations.
In 2010, `r location2` have 7 and above locations.

Comment: In 2002, `r pull(sub8,locationabbr)` have respectively `r pull(sub8,n)` observations.
In 2010, `r pull(sub10,locationabbr)` have respectively `r pull(sub10,n)` observations.

## Second
```{r}
sub11=sub6 %>% 
  filter(response=="Excellent")%>% 
  group_by(locationabbr,year) %>% 
  mutate(ave=mean(data_value)) %>% 
 select(year,locationabbr,ave)
  
p1=ggplot(sub11,aes(x=year,y=ave, color = locationabbr))+geom_line()+ scale_color_hue(name = "State")
p1
```

Comment: The WV state have the lowest value of spaghetti during 2002-2010. And the values of spaghetti in each state were not stable during those years.

## Third 
```{r}
sub12=sub6 %>% 
  filter(locationabbr=="NY"&year %in% c("2006","2010")  ) %>% 
 select(data_value,response,locationdesc,year)
sub12 %>% 
  mutate(
    locationdesc=recode(locationdesc,"NY - Bronx County"="Bronx","NY - Erie County"="Eric",	"NY - Kings County"="Kings","NY - Monroe County"="Monroe",	"NY - New York County"="New York","NY - Nassau County"="Nassau","NY - Queens County"="Queens","NY - Suffolk County"="Suffolk","NY - Westchester County"="Westchester"))%>% 
  ggplot(aes(x=locationdesc,y=data_value,color=response,group=response))+
  geom_point()+geom_line()+theme(axis.text.x = element_text(angle = 60, hjust=1),legend.position = "bottom")+
  facet_grid(.~year)
```

Comment:
The Poor response in both 2006 and 2010 had very low values among all locations. The good and very good responses had high values both in 2006 and 2010 in all locations. While the Excellent response, occupied the middle position, not having very high values nor low values in every location. 

